Quality measure notes

### 2021-07-26 StateOfPractice/Ao-Report/11Introduction.tex
MI report - added ch 1 and ch 6

\chapter{Introduction}
\label{ch_intro}

introduction

>>>>

\chapter{Introduction}
\label{ch_intro}
This paper analyzes the state of the practice for Medical Imaging (MI) software. MI is the clinical tool to image the interior of a body, providing information for diagnostic, analytic, and medical applications \cite{FDA2021} \cite{enwiki:1034887445}. MI is an essential part of collecting accurate information during clinical diagnosis \cite{Zhang2008}. MI computing and software aim to visualize and process medical images and produce clinically meaningful information \cite{enwiki:1034877594}.

Scientiﬁc computing (SC) is the technique and process of mathematically modeling real-world engineering or scientific systems with computing tools, as well as analysis and prediction with the models \cite{Smith2006}. MI software belongs to a specific domain of SC.

We aim to study the current status of SC software development in the MI domain; understand the current merits, drawbacks, and pain points during the development process, as well as the software qualities in the domain; provide guidelines and recommendations for future development.

Section \ref{sec_motivation} presents our motivation to start the research set the above goals, Section \ref{sec_research_questions} lists our research questions, and Section \ref{sec_scope} explains the domain analysis of MI software scope of our research.

\section{Motivation}
\label{sec_motivation}
Most scientists think developing and using SC software play significant roles in their research \cite{Hannay2009}. They spend a substantial proportion of their working hours on SC software development \cite{Hannay2009} \cite{Prabhu2011}, and this proportion of time has increased over the years \cite{Hannay2009}.

Developing SC software requires solid knowledge in specific domains \cite{Wilson2014}. Many of them learn software engineering skills by themselves or from their peers, instead of proper training \cite{Hannay2009}. Hannay et al. \cite{Hannay2009} also pointed out that many scientists showed ignorance and indifference to standard software engineering concepts. According to a survey by Prabhu et al. \cite{Prabhu2011}, more than half of the 114 subjects did not use any proper debugger for their software.

Due to its nature, SC software born from one project can be part of many other projects in the future, with the potential to disproportionately causing damages to scientific researches \cite{Wilson2014}.

As a result, the development process and quality of SC software concern us. We want to understand their status in SC domains and improve them.

\section{Research Questions}
\label{sec_research_questions}
To achieve our objectives, we designed a few research questions and tried to answer them by our research methods. The questions are as follows,

\begin{enumerate}
\item What are the pain points for developers working on MI software projects? What are the solutions for these pain points?
\item What artifacts the projects generated?
\item What role does documentation play in the projects? What are the developers' attitudes toward it?
\item What principles, processes, methodologies, and tools the projects used?
\item What is the current status of the following software qualities for the projects? What actions have the developers taken to address them?
\begin{itemize}
	\item Installability
	\item Correctness \& Verifiability
	\item Reliability
	\item Robustness
	\item Usability
	\item Maintainability
	\item Reusability
	\item Understandability
	\item Visibility/Transparency
\end{itemize}
\item How does software quality ranking generated by our methods compare with the ratings from the community?
\end{enumerate}

\section{Scope}
\label{sec_scope}
According to Bankman \cite{Bankman2000}, MI software deals with six different basic problems, while Angenentet et al. \cite{Angenent2006} pointed out that four fundamental problems are solved by MI software. While both mentioned Segmentation, Registration, and Visualization of medical images, Bankman also included Enhancement, Quantification, and a section covering some other functions \cite{Bankman2000}. On the other hand, Angenent's team included Simulation \cite{Angenent2006}. According to Wikipedia contributors \cite{enwiki:1034877594}, MI software has primary functions in categories such as Segmentation, Registration, Visualization (including the basic display, reformatted views, and 3D volume rendering), Statistical Analysis, Image-based Physiological Modelling, etc. As Kim et al. \cite{Kim2011} describe, the general steps of medical image analysis after obtaining digital data include Enhancement, Segmentation, Feature Extraction, Classification, and Interpretation. Besides the above major functions, some MI software provides supportive functions. For example, with Tool Kit libraries VTK \cite{SchroederEtAl2006} and ITK \cite{McCormick2014}, developers build software with Visualization and Analysis functions; Picture Archiving and Communication System (PACS) helps users to economically store and conveniently access images \cite{Choplin1992}.

We divided MI software into five sub-groups and several sub-sub-groups by their major functions shown in Figure \ref{fig_mi_functions}.

\begin{figure}
\centering
\begin{tikzpicture}[mindmap, grow cyclic, every node/.style=concept, concept
color=orange!40,
level 1/.append style={level distance=5cm,sibling angle=72},
level 2/.append style={level distance=3cm,sibling angle=90},
level 3/.style={level distance=2.3cm,sibling angle=90}]
\node{MI software}
child[concept color=teal!40] { node {Enhancement}}
child[concept color=teal!40] { node {Analysis}
    child[concept color=blue!30] { node {Registration}}
    child[concept color=blue!30,] { node {Segmentation}}
    child[concept color=blue!30] { node {Statistical Analysis}
    child[concept color=blue!20] { node {Feature Extraction}}
    child[concept color=blue!20] { node {Classification}}
    child[concept color=blue!20] { node {Interpretation}}
    }}
child[concept color=teal!40] { node {Simulation/\\Modeling}}
child[concept color=teal!40] { node {Supporting}
    child[concept color=blue!30] { node {Tool Kit}}
    child[concept color=blue!30] { node {PACS}}
}
child[concept color=teal!40] { node {Visualization}
    child[concept color=blue!30] { node {2D Display}}
    child[concept color=blue!30] { node {3D Rendering}}
    child[concept color=blue!30] { node {Reformatted Views}}
};
\end{tikzpicture}
\caption{Major functions of MI software}
\label{fig_mi_functions}
\end{figure}

In this project, the scope of the software is limited to the software library providing the Visualization tools and functions.

### 2021-07-26 StateOfPractice/Ao-Report/13Methods.tex
MI report - added ch 1 and ch 6

\section{Applying the Method to Medical Imaging (MI)}
\label{sec_applying_method}

Based on the principles in Section \ref{sec_domain_selection}, we selected the MI domain and the viewer sub-group. We also included MI domain experts in our team.

@@

Appendix \ref{ap_list_before_filtering} shows all the 48 software packages. Among them, there were several ones that we could not find in their source code, such as \textit{MicroDicom}, \textit{Aliza}, and \textit{jivex}, etc. These packages are likely to be freeware defined in Section \ref{sec_freeware} and not OSS. So following guidelines in Section \ref{sec_filter_software_list} we removed them from the list. Next, we focused on the MI software that could work as a MI viewer. Some of the software on the list were tool kits or libraries for other software to use as dependencies but not for end-users to view medical images, such as \textit{VTK}, \textit{ITK}, \textit{dcm4che}, etc. We also eliminated these from the list. After that, there were 29 software products left on the list. We still preferred projects using git and GitHub and being updated recently, but did not apply another filtering since the number of packages was already below 30. However, 27 out of the 29 software packages on the final list used git, and 24 chose GitHub. Furthermore, 27 packages had the latest updates after the year 2018, and 23 after 2020.

>>>>

\section{Applying the Method to MI}
\label{sec_applying_method}

Based on the principles in Section \ref{sec_domain_selection}, we selected the MI domain and the sub-group of software with Visualization function shown in Figure \ref{fig_mi_functions}. We also included MI domain experts in our team.

@@

Appendix \ref{ap_list_before_filtering} shows all the 48 software packages. Among them, there were several ones that we could not find in their source code, such as \textit{MicroDicom}, \textit{Aliza}, and \textit{jivex}, etc. These packages are likely to be freeware defined in Section \ref{sec_freeware} and not OSS. So following guidelines in Section \ref{sec_filter_software_list} we removed them from the list. Next, we focused on the MI software providing visualization functions. Some of the software on the list were tool kits or libraries for other software to use as dependencies but not for end-users to view medical images, such as \textit{VTK}, \textit{ITK}, \textit{dcm4che}, etc. We also eliminated these from the list. After that, there were 29 software products left on the list. We still preferred projects using git and GitHub and being updated recently, but did not apply another filtering since the number of packages was already below 30. However, 27 out of the 29 software packages on the final list used git, and 24 chose GitHub. Furthermore, 27 packages had the latest updates after the year 2018, and 23 after 2020.

### 2021-07-26 StateOfPractice/Ao-Report/16ThreatToValidity.tex
MI report - added ch 1 and ch 6

\begin{itemize}
\item limited time to each software, surface quality
\item impressions, subjective
\item searched all information by ourselves, so maybe missed some info
\item mainly measured by one person, so maybe biased
\end{itemize}

>>>>

This section lists all the potential threats to the validity of our research.

\begin{enumerate}
\item We compared nine software qualities for 29 software packages, so we could only spend a limited time on each of them. As a result, our assessments may not be thorough in revealing their status fully.
\item We used the grading template in Appendix \ref{ap_grading_template} to guide our measurements. Our impressions of the software - such as user experience - were factors in deciding some scores. Thus, there is a risk that some scores may be subjective and biased.
\item It was not practical to ask each development team for every piece of information. We collected much information - such as artifacts and funding situations of software - by ourselves. There may be cases that we missed some information.
\item We interviewed eight teams, which is a good proportion of the 29. However, there is still a risk that they might not well represent the whole MI software community.
\item As mentioned in Section \ref{ch_interview}, one interviewee was too busy to participate in a full interview, so he provided a version of written answers to us. Since we did not have the chance to explain our questions or ask him follow-up questions, there is a possibility of misinterpretation of the questions or answers.
\end{enumerate}

### 2021-07-26 StateOfPractice/Ao-Report/32FullSoftwareListBeforeFiltering.tex
MI report - update styles
MI report - added ch 1 and ch 6

Table \ref{tab_list_before_filtering} lists the 48 software before filtering. We selected 29 of them to the final list, which are all open-source and in the same sub-group. We divided them into four sub-groups: Viewer (V), Tool Kit (TK), Picture Archiving and Communication System (PACS), and Convertion (C). The table also shows the sources of identifying them.

\begin{table}[]
	\begin{tabular}{lllllllllll}
		\hline
		&  &  &  & \multicolumn{7}{c}{Source} \\ \cline{5-11} 
		\multirow{-2}{*}{Software} & \multirow{-2}{*}{\begin{tabular}[c]{@{}l@{}}Final\\ list\end{tabular}} & \multirow{-2}{*}{\begin{tabular}[c]{@{}l@{}}Open-\\ source\end{tabular}} & \multirow{-2}{*}{\begin{tabular}[c]{@{}l@{}}Sub-\\ group\end{tabular}} & \cite{Bjorn2017} & \cite{Bruhschwein2019} & \cite{Haak2015} & \cite{Emms2019} & \cite{Hasan2020} & \cite{Mu2019} & \cite{Samala2014} \\ \hline
		3D Slicer \cite{Kikinis2014} & X & X & V &  &  & X & X & X &  & X \\
		Ginkgo CADx \cite{Wollny2020} & X & X & V & X & X & X & X & X & X &  \\
		XMedCon \cite{Nolf2003} & X & X & V &  &  & X & X & X & X &  \\
		Weasis \cite{Roduit2021} & X & X & V &  &  & X & X & X & X &  \\
		MRIcroGL \cite{Rorden2021} & X & X & V &  &  & X & X & X &  & X \\
		SMILI \cite{Chandra2018} & X & X & V &  &  &  & X & X & X &  \\
		ImageJ \cite{Rueden2017} & X & X & V &  &  & X & X & X &  & X \\
		Fiji \cite{Schindelin2012} & X & X & V &  &  &  &  &  &  & X \\
		DicomBrowser \cite{Archie2012} & X & X & V &  &  &  & X & X &  &  \\
		3DimViewer \cite{TESCAN2020} & X & X & V & X &  &  & X & X &  &  \\
		Horos \cite{horosproject2020} & X & X & V & X & X &  &  &  &  &  \\
		OsiriX Lite \cite{PixmeoSARL2019} & X & X & V & X & X & X &  &  &  &  \\
		dwv \cite{Martelli2021} & X & X & V & X &  & X &  &  &  &  \\
		Drishti \cite{Limaye2012} & X & X & V & X &  &  &  &  &  &  \\
		\begin{tabular}[c]{@{}l@{}}BioImage Suite\\ Web \cite{Papademetris2005} \end{tabular} & X & X & V &  &  & X &  &  &  &  \\
		OHIF Viewer \cite{Ziegler2020} & X & X & V & \multicolumn{7}{l}{Other source: \cite{Ziegler2020}} \\
		Slice:Drop \cite{Haehn2013} & X & X & V &  &  & X &  &  &  &  \\
	\end{tabular}
\end{table}

\begin{table}[]
	\begin{tabular}{lllllllllll}
		\hline
		&  &  &  & \multicolumn{7}{c}{Source} \\ \cline{5-11} 
		\multirow{-2}{*}{Software} & \multirow{-2}{*}{\begin{tabular}[c]{@{}l@{}}Final\\ list\end{tabular}} & \multirow{-2}{*}{\begin{tabular}[c]{@{}l@{}}Open-\\ source\end{tabular}} & \multirow{-2}{*}{\begin{tabular}[c]{@{}l@{}}Sub-\\ group\end{tabular}} & \cite{Bjorn2017} & \cite{Bruhschwein2019} & \cite{Haak2015} & \cite{Emms2019} & \cite{Hasan2020} & \cite{Mu2019} & \cite{Samala2014} \\ \hline
		GATE \cite{Jan2004} & X & X & V &  &  &  & X &  &  &  \\
		ITK-SNAP \cite{Yushkevich2006} & X & X & V &  &  &  &  &  &  & X \\
		ParaView \cite{Ahrens2005} & X & X & V &  &  &  &  &  &  & X \\
		MatrixUser \cite{Liu2016} & X & X & V &  &  &  &  & X &  &  \\
		DICOM Viewer \cite{Afsar2021} & X & X & V &  &  &  &  & X &  &  \\
		INVESALIUS 3 \cite{Amorim2015} & X & X & V &  &  &  &  & X &  &  \\
		medInria \cite{Fillard2012} & X & X & V &  &  & X &  &  &  &  \\
		dicompyler \cite{Panchal2010} & X & X & V &  &  &  &  &  & X &  \\
		MicroView \cite{ParallaxInnovations2020} & X & X & V &  &  & X &  &  &  &  \\
		Papaya \cite{UTHSCSA2019} & X & X & V &  &  &  & X & X & X &  \\
		AMIDE \cite{Loening2017} & X & X & V &  &  &  & X & X & X &  \\
		Gwyddion \cite{Nevcas2012} & X & X & V &  &  &  &  & X &  &  \\
		VTK \cite{SchroederEtAl2006} &  & X & TK &  &  &  &  &  &  & X \\
		ITK \cite{McCormick2014} &  & X & TK &  &  &  &  &  &  & X \\
		DCMTK \cite{DCMTK2021} &  & X & TK &  &  &  &  & X & X &  \\
		XTK \cite{Haehn2012} &  & X & TK & \multicolumn{7}{l}{Other source: it is used by slice:drop} \\
		dcm4che \cite{dcm4che2021} &  & X & TK & X &  &  & X & X &  &  \\
		cornerstone \cite{cornerstone2020} &  & X & TK &  &  & X &  &  &  &  \\
	\end{tabular}
\end{table}

\begin{table}[]
	\begin{tabular}{lllllllllll}
		\hline
		&  &  &  & \multicolumn{7}{c}{Source} \\ \cline{5-11} 
		\multirow{-2}{*}{Software} & \multirow{-2}{*}{\begin{tabular}[c]{@{}l@{}}Final\\ list\end{tabular}} & \multirow{-2}{*}{\begin{tabular}[c]{@{}l@{}}Open-\\ source\end{tabular}} & \multirow{-2}{*}{\begin{tabular}[c]{@{}l@{}}Sub-\\ group\end{tabular}} & \cite{Bjorn2017} & \cite{Bruhschwein2019} & \cite{Haak2015} & \cite{Emms2019} & \cite{Hasan2020} & \cite{Mu2019} & \cite{Samala2014} \\ \hline
		orthanc \cite{Jodogne2018} &  & X & PACS & X &  &  &  & X &  &  \\
		Conquest \cite{Herk2021} &  & X & PACS & X &  &  &  &  &  &  \\
		ClearCanvas \cite{ClearCanvas2015} &  & X & PACS, V & X &  &  &  &  &  &  \\
		dcm2niix \cite{Li2016} &  & X & C &  &  &  &  & X &  &  \\
		\begin{tabular}[c]{@{}l@{}}Open Dicom\\ Viewer \cite{OpenDicomViewer2011} \end{tabular} &  & X & V &  &  & X &  &  & X &  \\
		MicroDicom \cite{MicroDicom2021} &  &  & V & X &  &  &  &  & X &  \\
		Aliza \cite{Aliza2021} &  &  & V &  &  &  & X &  & X &  \\
		JiveX \cite{Visus2021} &  &  & V &  &  & X &  &  & X &  \\
		MIPAV \cite{CIT2020} &  &  & V &  &  & X &  &  &  &  \\
		Oviyam \cite{RasterImages2021} &  &  & V &  &  & X &  &  &  &  \\
		MeVisLab \cite{Heckel2009} &  &  & V &  &  &  &  &  &  & X \\
		\begin{tabular}[c]{@{}l@{}}Sante DICOM\\ Viewer Lite \cite{Santesoft2021} \end{tabular} &  &  & V &  &  &  &  &  & X &  \\
		\begin{tabular}[c]{@{}l@{}}Navegatium\\ DICOM Viewer\end{tabular} &  &  & V &  &  &  &  &  & X &  \\ \hline
	\end{tabular}
	\caption{\label{tab_list_before_filtering}Full software list before filtering}
\end{table}

>>>>

Table \ref{tab_list_before_filtering} lists the 48 software before filtering. We selected 29 of them to the final list, which are all open-source and in Visualization (V) sub-group. We found software packages in sub-groups Tool Kit (TK) and PACS but removed them from the final list. The table also shows the sources of identifying them.

\begin{table}[H]
\begin{tabular}{lllllllllll}
\hline
 &  &  &  & \multicolumn{7}{c}{Source} \\ \cline{5-11} 
\multirow{-2}{*}{Software} & \multirow{-2}{*}{\begin{tabular}[c]{@{}l@{}}Final\\ list\end{tabular}} & \multirow{-2}{*}{\begin{tabular}[c]{@{}l@{}}Open-\\ source\end{tabular}} & \multirow{-2}{*}{\begin{tabular}[c]{@{}l@{}}Sub-\\ group\end{tabular}} & \cite{Bjorn2017} & \cite{Bruhschwein2019} & \cite{Haak2015} & \cite{Emms2019} & \cite{Hasan2020} & \cite{Mu2019} & \cite{Samala2014} \\ \hline
3D Slicer \cite{Kikinis2014} & X & X & V &  &  & X & X & X &  & X \\
Ginkgo CADx \cite{Wollny2020} & X & X & V & X & X & X & X & X & X &  \\
XMedCon \cite{Nolf2003} & X & X & V &  &  & X & X & X & X &  \\
Weasis \cite{Roduit2021} & X & X & V &  &  & X & X & X & X &  \\
MRIcroGL \cite{Rorden2021} & X & X & V &  &  & X & X & X &  & X \\
SMILI \cite{Chandra2018} & X & X & V &  &  &  & X & X & X &  \\
ImageJ \cite{Rueden2017} & X & X & V &  &  & X & X & X &  & X \\
Fiji \cite{Schindelin2012} & X & X & V &  &  &  &  &  &  & X \\
DicomBrowser \cite{Archie2012} & X & X & V &  &  &  & X & X &  &  \\
\end{tabular}
\end{table}

\begin{table}[H]
\begin{tabular}{lllllllllll}
\hline
 &  &  &  & \multicolumn{7}{c}{Source} \\ \cline{5-11} 
\multirow{-2}{*}{Software} & \multirow{-2}{*}{\begin{tabular}[c]{@{}l@{}}Final\\ list\end{tabular}} & \multirow{-2}{*}{\begin{tabular}[c]{@{}l@{}}Open-\\ source\end{tabular}} & \multirow{-2}{*}{\begin{tabular}[c]{@{}l@{}}Sub-\\ group\end{tabular}} & \cite{Bjorn2017} & \cite{Bruhschwein2019} & \cite{Haak2015} & \cite{Emms2019} & \cite{Hasan2020} & \cite{Mu2019} & \cite{Samala2014} \\ \hline
3DimViewer \cite{TESCAN2020} & X & X & V & X &  &  & X & X &  &  \\
Horos \cite{horosproject2020} & X & X & V & X & X &  &  &  &  &  \\
OsiriX Lite \cite{PixmeoSARL2019} & X & X & V & X & X & X &  &  &  &  \\
dwv \cite{Martelli2021} & X & X & V & X &  & X &  &  &  &  \\
Drishti \cite{Limaye2012} & X & X & V & X &  &  &  &  &  &  \\
\begin{tabular}[c]{@{}l@{}}BioImage Suite\\ Web \cite{Papademetris2005} \end{tabular} & X & X & V &  &  & X &  &  &  &  \\
OHIF Viewer \cite{Ziegler2020} & X & X & V & \multicolumn{7}{l}{Other source: \cite{Ziegler2020}} \\
Slice:Drop \cite{Haehn2013} & X & X & V &  &  & X &  &  &  &  \\
GATE \cite{Jan2004} & X & X & V &  &  &  & X &  &  &  \\
ITK-SNAP \cite{Yushkevich2006} & X & X & V &  &  &  &  &  &  & X \\
ParaView \cite{Ahrens2005} & X & X & V &  &  &  &  &  &  & X \\
MatrixUser \cite{Liu2016} & X & X & V &  &  &  &  & X &  &  \\
DICOM Viewer \cite{Afsar2021} & X & X & V &  &  &  &  & X &  &  \\
INVESALIUS 3 \cite{Amorim2015} & X & X & V &  &  &  &  & X &  &  \\
medInria \cite{Fillard2012} & X & X & V &  &  & X &  &  &  &  \\
dicompyler \cite{Panchal2010} & X & X & V &  &  &  &  &  & X &  \\
MicroView \cite{ParallaxInnovations2020} & X & X & V &  &  & X &  &  &  &  \\
Papaya \cite{UTHSCSA2019} & X & X & V &  &  &  & X & X & X &  \\
AMIDE \cite{Loening2017} & X & X & V &  &  &  & X & X & X &  \\
Gwyddion \cite{Nevcas2012} & X & X & V &  &  &  &  & X &  &  \\
VTK \cite{SchroederEtAl2006} &  & X & TK &  &  &  &  &  &  & X \\
ITK \cite{McCormick2014} &  & X & TK &  &  &  &  &  &  & X \\
\end{tabular}
\end{table}

\begin{table}[H]
\begin{tabular}{lllllllllll}
\hline
 &  &  &  & \multicolumn{7}{c}{Source} \\ \cline{5-11} 
\multirow{-2}{*}{Software} & \multirow{-2}{*}{\begin{tabular}[c]{@{}l@{}}Final\\ list\end{tabular}} & \multirow{-2}{*}{\begin{tabular}[c]{@{}l@{}}Open-\\ source\end{tabular}} & \multirow{-2}{*}{\begin{tabular}[c]{@{}l@{}}Sub-\\ group\end{tabular}} & \cite{Bjorn2017} & \cite{Bruhschwein2019} & \cite{Haak2015} & \cite{Emms2019} & \cite{Hasan2020} & \cite{Mu2019} & \cite{Samala2014} \\ \hline
DCMTK \cite{DCMTK2021} &  & X & TK &  &  &  &  & X & X &  \\
XTK \cite{Haehn2012} &  & X & TK & \multicolumn{7}{l}{Other source: it is used by slice:drop} \\
dcm4che \cite{dcm4che2021} &  & X & TK & X &  &  & X & X &  &  \\
cornerstone \cite{cornerstone2020} &  & X & TK &  &  & X &  &  &  &  \\
dcm2niix \cite{Li2016} &  & X & TK &  &  &  &  & X &  &  \\
orthanc \cite{Jodogne2018} &  & X & PACS & X &  &  &  & X &  &  \\
Conquest \cite{Herk2021} &  & X & PACS & X &  &  &  &  &  &  \\
ClearCanvas \cite{ClearCanvas2015} &  & X & PACS, V & X &  &  &  &  &  &  \\
\begin{tabular}[c]{@{}l@{}}Open Dicom\\ Viewer \cite{OpenDicomViewer2011} \end{tabular} &  & X & V &  &  & X &  &  & X &  \\
MicroDicom \cite{MicroDicom2021} &  &  & V & X &  &  &  &  & X &  \\
Aliza \cite{Aliza2021} &  &  & V &  &  &  & X &  & X &  \\
JiveX \cite{Visus2021} &  &  & V &  &  & X &  &  & X &  \\
MIPAV \cite{CIT2020} &  &  & V &  &  & X &  &  &  &  \\
Oviyam \cite{RasterImages2021} &  &  & V &  &  & X &  &  &  &  \\
MeVisLab \cite{Heckel2009} &  &  & V &  &  &  &  &  &  & X \\
\begin{tabular}[c]{@{}l@{}}Sante DICOM\\ Viewer Lite \cite{Santesoft2021} \end{tabular} &  &  & V &  &  &  &  &  & X &  \\
\begin{tabular}[c]{@{}l@{}}Navegatium\\ DICOM Viewer\end{tabular} &  &  & V &  &  &  &  &  & X &  \\ \hline
\end{tabular}
\caption{\label{tab_list_before_filtering}Full software list before filtering}
\end{table}
